\documentclass[11pt,letterpaper,english]{article}
\usepackage[T1]{fontenc} % Standard package for selecting font encodings
\usepackage{txfonts} % makes spacing between characters space correctly
\usepackage{xcolor} % Driver-independent color extensions for LaTeX and pdfLaTeX.
%\usepackage{blindtext} % To create text
%\usepackage{mdwlist} % mdwlist for compact enumeration/list items 
%\usepackage[pagestyles]{titlesec} % related with sections—namely titles, headers and contents
%\usepackage{fancyhdr} % header footer placement

\usepackage[top=1in, bottom=1in, left=1in, right=1in] {geometry} % Margins
\usepackage{graphicx}   % Essential for adding images to you document.

\usepackage{sectsty}
\sectionfont{\large}
\subsectionfont{\normalsize}
\subsubsectionfont{\normalsize \it}

\usepackage{caption}
\captionsetup{labelsep=period}

%\pagestyle{fancy} % allows you to use the header and footer commands 

\raggedright
\begin{document}

\setlength{\parindent}{0in} % Amount of indentation at the first line of a paragraph.

%\pagestyle{fancy} \lhead{Title} \rhead{Lead PI} \renewcommand{%
%\headrulewidth}{0.0pt}



\centering {
{\bf Andrew J. Nonaka}\\
{\bf Lawrence Berkeley National Laboratory \\
MS 50A-1148 \\
Berkeley, CA 94720 \\
AJNonaka@lbl.gov \\
510-486-7107} \smallskip

\begin{flushleft} {\bf Professional Preparation}
{\parindent 12pt

Ph.D. in Engineering Applied Science, U.C. Davis, 2007. \\
M.S. in Engineering Applied Science, U.D. Davis, 2004. \\
B.S. in Electrical Engineering, University of the Pacific, 2002. \\
}

\vspace{.04in}
{\bf Appointments}
{\parindent 12pt

2011--present Research Scientist, Center for Computational Sciences and Engineering, LBNL \\ 
2013--present Adjunct Lecturer, School of Engineering and Computer Science, University of the Pacific \\
2007--2011    Postdoc, Center for Computational Sciences and Engineering, LBNL \\ 
2003--2007    Student Employee Graduate Researcher, Institute for Scientific Computing Research, LLNL \\
2003--2007    Guest Research, Applied Numerical Algorithms Group, LBNL \\
}

\vspace{.04in}
{\bf Five Publications Most Relevant to This Proposal}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt

\item A. Nonaka, A. S. Almgren, J. B. Bell, M. J. Lijewski, C. M. Malone, and M. Zingale,
\newblock {\tt MAESTRO}: An Adaptive Low Mach Number Hydrodynamics Algorithm for
  stellar flows.
\newblock {\em Astrophysical Journal Supplement}, 
\newblock {\bf 188}, 358, 2010. \\ 

\item A. Nonaka, A. J. Aspden, M. Zingale, A. S. Almgren, J. B. Bell, and S. E. Woosley,
\newblock High-Resolution Simulations of Convection Preceding Ignition in Type Ia Supernovae Using Adaptive Mesh Refinement
\newblock {\em Combustion Theory and Modelling},
\newblock {\bf 16}, 6, 1053, 2012. \\ 

\item A. Nonaka, J. B. Bell, M. S. Day, C. Gilet, A. S. Almgren, and M. L. Minion,
\newblock A Deferred Correction Coupling Strategy for Low Mach Number Flow with Complex Chemistry
\newblock {\em Astrophysical Journal}, 
\newblock {\bf 745}, 73, 2012. \\ 

\item A. S. Almgren, V. E. Beckner, J. B. Bell, M. S. Day, L. H. Howell, C. C. Joggerst, M. J. Lijewski, A. Nonaka, M. Singer, and M. Zingale
\newblock {\tt CASTRO}: A New Compressible Astrophysical Solver. I. Hydrodynamics and Self-Gravity
\newblock {\em Astrophysical Journal}, 
\newblock {\bf 715}, 1221, 2010. \\ 

\item C. M. Malone, A. Nonaka, S. E. Woosley, A. S. Almgren, J. B. Bell, S. Dong, and M. Zingale, 
\newblock{ The Deflagration Stage of Chandrasekhar Mass Models for Type Ia Supernovae: I. Early Evolution},
\newblock{\em Astrophysical Journal}, \newblock{\bf 782}, 11, 2014.  \\ 

\end{enumerate} 

\vspace{-6pt}
{\bf Research Interests and Expertise}
{\parindent 12pt

My research focuses on efficient and scalable numerical methods for complex multiphysics applications described by time-dependent ordinary
and partial differential equations.  My current investigations include the following:
(1) Development of high-resolution, spatially and temporally adaptive numerical methods for the study of compressible, incompressible, 
and low Mach number reacting flow,
(2) Multiphysics coupling strategies for both terrestrial and astrophysical combustion,
(3) Numerical studies of the convection and ignition phase of Type Ia supernovae,
(4) Parallel performance for finite-volume adaptive mesh refinement algorithms on massively parallel architectures.
}

%Synergistic Activities. A list of up to five examples that demonstrate
%the broader impact of the individual's professional and scholarly
%activities that focuses on the integration and transfer of knowledge
%as well as its creation.

\newpage

{\bf Synergistic Activities}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item Reviewer: CAMCoS, IJNME, HPC Grant Proposals

\end{enumerate} 

\vspace{-6pt}
{\bf Collaborators ({\emph{past 5 years including name and current institution}})} 
{\parindent 12pt

A. Almgren (LBNL),
A. Aspden (Southhampton),
V. Beckner (LBNL),
J. Bell (LBNL),
A. Bhattacharjee (IISc Bangalore),
M. Cai (Courant),
R. Cisneros (NCSA),
S. Dong (UCSC),
A. Garcia (SJSU),
C. Gilet (Michigan),
B. Griffith (UNC),
M. Day (LBNL),
A. Donev (Courant),
T. Fai (Harvard),
A. Jacobs (Stony Brook),
H. Ma (UCSC),
C. Malone (LANL), 
S. May (Dortmund),
M. Minion (LBNL),
R. Orvedahl (Boulder),
W. Pazner (UC Berkeley),
Y. Sun (Courant),
S. Woosley (UCSC),
M. Zingale (Stony Brook),
W. Zhang (LBNL)

}


\end{flushleft}

\end{document}
