\documentclass[11pt,letterpaper,english]{article}
\usepackage[T1]{fontenc} % Standard package for selecting font encodings
\usepackage{txfonts} % makes spacing between characters space correctly
\usepackage{xcolor} % Driver-independent color extensions for LaTeX and pdfLaTeX.
\usepackage{hyperref}  %The ability to create hyperlinks within the document
\usepackage{multicol}
\usepackage{fancyhdr} % header footer placement

\usepackage[top=1in, bottom=1in, left=1in, right=1in] {geometry} % Margins
\usepackage{graphicx}   % Essential for adding images to you document.

\usepackage[numbers]{natbib}

%\usepackage{sectsty}
%% \sectionfont{\normalsize}
%% \subsectionfont{\normalsize}
%\subsubsectionfont{\normalsize \it}

\usepackage[small,compact]{titlesec}
\titlespacing{\section}{0pt}{0.5em}{0.25em}
\titlespacing{\subsection}{0pt}{0.5em}{0.125em}
\titlespacing{\subsubsection}{0pt}{0.5em}{0.25em}
\titlespacing{\paragraph}{0pt}{0.5em}{0.5em}

\setlength{\textfloatsep}{7pt}

\titleformat*{\subsubsection}{\itshape}

\let\oldthebibliography=\thebibliography
  \let\endoldthebibliography=\endthebibliography
  \renewenvironment{thebibliography}[1]{%
    \begin{oldthebibliography}{#1}%
      \setlength{\parskip}{0.1ex}% 
      \setlength{\itemsep}{0.0ex}% 
  }%
  {% 
    \end{oldthebibliography}% 
  }


% commas between multiple footnotes
\newcommand\fnsep{\textsuperscript{,}}

\usepackage{caption}
\captionsetup{labelsep=period}

\setlength{\parskip}{0.1\baselineskip}%
%\setlength{\parindent}{0pt}%

\input newcommands

%\raggedright

\begin{document}

\pagestyle{fancy} 
\lhead{Approaching Exascale Models of Astrophysical Explosions} 
\rhead{PI: Zingale} \renewcommand{%
\headrulewidth}{0.0pt}

\begin{center}
{\bf PROJECT NARRATIVE}
\end{center}


%-----------------------------------------------------------------------------
\section{SIGNIFICANCE OF RESEARCH}

%% Explain what advances you expect to be enabled by an INCITE award that
%% justifies an allocation of petascale resources (e.g., anticipated
%% impact on community paradigms, valuable insights into or solving a
%% long-standing challenge, etc). Place the proposed research in the
%% context of competing work in your discipline or business. The
%% information should be sufficient for peer review in your area of
%% research and also appropriate for general scientific review comparing
%% your proposal with proposals in other disciplines. Potential impact is
%% the predominant determinant for awards. This factor will be assessed
%% by a peer-review panel. Also list any previous INCITE award(s)
%% received and discuss the relationship to the work proposed. {\bf This
%%   section is typically about 4 pages.}

We propose a collaborative investigation of multiple types of stellar
explosions and their precursors using a suite of state-of-the-art
hydrodynamics codes.  Several progenitor models of SNe Ia will be
explored, including their pre-explosion and explosive phases, using
our codes \maestro, \castro, and \flash.  XRBs will also be studied in
their pre-explosive and explosive phases, using \maestro\ and \castro.
The curious radiation-dominated systems like the BWP will be explored
with \castro, and ccSNe will be studied using \chimera.  All
calculations will be 3D and face the challenges of capturing the
effects of turbulence, instabilities, strong gravitational
interactions, nuclear reactions, and radiation.  These challenges make
these problems INCITE-class, and only the resources Titan can provide
will enable use to further our understanding.  Despite the broad suite
of codes, there are common links, namely in the microphysics
(reactions, equations of state) and in our shared approach to
utilitizing the GPUs on Titan.  This collaboration is an expansion of
our existing INCITE proposal, but we believe that it represents the
most efficient use of resources, allowing us to work together as a
team to create portable solvers to effectively make use of this
architecture and its successor.  These GPU-enabled solvers will be
made freely available.

Our publication record demonstrates that we have made productive use
of our current INCITE award, and we expect similar productivity
carrying forward.  Furthermore, this INCITE time will help train
the next generation of computational scientists---graduate students
feature prominently in the proposed work plan.


\subsection{Type Ia supernovae}

\input sneIa.tex


\subsection{Type I X-ray bursts}

\input xrb.tex


\subsection{Core-collapse supernovae}

\input ccsne.tex


\subsection{Black-widow pulsars}

\input bwp.tex


\subsection{Application Codes}

\paragraph{\maestro\ and \castro.}
%
The XRB, BWP, and most of the SNe Ia work will be performed with our
state-of-the-art simulation codes \maestro~\cite{multilevel} and
\castro~\cite{castro:I}, developed over the past 10 years in
collaboration with Lawrence Berkeley Lab.  \maestro\ is tuned to
efficiently model the highly subsonic convective flows that often
precede stellar explosions.  It accomplishes this by reformulating the
equations of hydrodynamics, filtering the soundwaves from the
equations of hydrodynamics, while keeping the compressibility effects
due to stratification and local heat release.  This allows it to take
much larger timesteps than traditional compressible codes.
\maestro\ has been used successfully to model the convection leading
to ignition in the Chandra model for SNe Ia, and will continue to be
used for the XRB, sub-Ch, and Urca convection simulations proposed
here.  \castro\ solves the fully compressible equations of
hydrodynamics, allowing it to model shocks and explosive phenomena.
It will be the simulation code for the WD mergers and flame
spreading on XRBs.  Considerable development has been done during the
current allocation period to allow \castro\ to accurate model gravity
and rotation for a pair of WDs~\cite{katz:2016}.  In later years, \castro\
will see a role in carrying our sub-Ch convection calculations into
the explosion phase.  \maestro\ and \castro\ share the underlying
microphysics e.g., equation of state (EOS) and nuclear reaction
networks, as well as the underlying \boxlib\ library that manages
their adaptive mesh refinement (AMR) grid hierarchy.  This makes it
straightforward to transition a problem from \maestro\ to \castro, as
was done during our previous INCITE allocation when studying flame
propagation in Chandra model SNe Ia~\cite{Mal14}.  Both codes are
already up and running on our target platform, Titan (OLCF).
Additionally, both codes are publicly available%
\footnote{https://github.com/BoxLib-Codes}---any performance or
physics improvements developed under this INCITE award will become
part of the public releases, benefiting the community at large.

\paragraph{\flash.}
%
%We will use the \flash\ code for some studies of the explosive phase
%of sub-Ch SNe Ia.  \MarginPar{Tom edit}
The FLASH code will be used to perform a subset of our SNe Ia work. FLASH is an adaptive-mesh, multi-physics code that solves the compressible equations of hydrodynamics. As part of our associated CAAR project, we recently installed the general thermonuclear reaction network, XNet, into FLASH, allowing us to evolve networks of arbitrary sizes. Using this new capability, we will study the effects of using improved nuclear kinetics during the explosive phase of sub-Ch SNe Ia.

\paragraph{\chimera}
%
\chimera\ will be used to model ccSNe.  
\chimera\ uses a directionally-split piecewise parabolic method (PPM) to solve the hydrodynamics. Self-gravity is computed via multipole expansion in spherical harmonics.The incorporated nuclear network, XNet, solves a system of coupled non-linear ODEs for the time evolution of the nuclear abundances independently for each zone. We also advect passive Lagrangian tracer particles through our simulation as data samplers to use in post-processing nucleosynthesis and other analyses. Transport of neutrinos is computed as multi-(energy)-group angular moments of the neutrino distribution function in a diffusive approximation flux-limited to prevent superluminal `diffusion' of neutrinos in semi-transparent and transparent regions (multi-group flux-limited diffusion, or MGFLD). 
Additional details about the architecture of \chimera\ can be found in \citep{brmehi09,Messeretal2012GPU}. A recent enhancement to \chimera\ for 3D has been the introduction of a Yin-Yang grid \citep{KageSato2004}, and 2 full-star 3D simulations are currently underway using this code as part of an associated PRAC allocation at Blue Waters. 

\subsection{Work under previous INCITE awards}

We are currently in the last year of a 2-year INCITE award at the OLCF
(AST106; PI: Zingale), focused on XRBs and SNe Ia.  Many of the
current investigators have also collaborated on previous INCITE
awards. 
The work on CCSNe proposed here follows work with \chimera\ under two previous INCITE awards (AST005 [2008-10; 2011-2013]  A. Mezzacappa, PI).  It also follows closely on the heels of a recent ALCC award (NPH108, B. Messer, PI) where we have performed studies 
of 3D turbulence in realistic CCSNe environments in an attempt to quantify the requisite spatial resolution. 

\paragraph{\maestro\ sub-Ch convection models.}
%
We completed the broadest 3D study to date of convection in the He layer
on sub-Ch WD, exploring a range of initial
models: core masses from 0.8 to 1.2~$M_\odot$ each with a range of He layer masses.
These 3D \maestro\ calculations showed a wide variety of outcomes:
a quasi-steady state, nova-like runaway over the entire layer, and 
localized thermonuclear runaway.  In all, over 70~Mh was
used to model this suite of calculations---a level of computational
power only achievable through INCITE.  The paper described these
results has been accepted to the Astrophysical
Journal~\cite{jacobs:2016}.  Figure~\ref{fig:current-runs} shows a
snapshot of one of these calculations.  The next suite of calculations building
off of the completed study is already underway in the current INCITE period.
These calculations will be more computationally expensive as we require
models of the full star as opposed to the previous study's focus on octants.

\paragraph{\castro\ WDWD models.}
%
In the current INCITE period, we have used Titan to help perform
a verification study of \castro\ for the case of WD mergers~\cite{katz:2016}.
We then used Titan to perform a suite of high resolution calculations
of white dwarf mergers and head-on collisions. These calculations have
helped us to further understand what techniques are necessary for
simulating these demanding events, in particular how to evolve the
nuclear reactions and also how to follow the dynamical in-fall of
one WD onto another due to gravitational tidal forces. These simulations
form the bulk of two papers which will soon be submitted to the
Astrophysical Journal.

\paragraph{\maestro\ XRB modules.}
%
We have completed the first-ever 3D calculation of convection in the
accreted layer on a NS as a model for the pre-explosion
phase of an XRB.  This calculation modeled a small portion of the star
(30~m on a side) with a mixed H/He layer, resolving the burning scales
(6 cm resolution) and evolving 11 isotopes describing hot-CNO burning
and some branches to the rp-process.  We demonstrated that the
convective layer becomes turbulent with a cascade that matches
Kolmogorov isotropic turbulence.

\paragraph{\chimera\ 3D CCSNe simulations.}

In 2013-2014, INCITE supported our pioneering efforts to run a single 3D, non-axisymmetric model with \chimera\. We evolved the simulation through 440~ms after core bounce.
The onset of explosion (shock revival) is delayed by $\sim$100~ms in 3D relative to the 2D counterpart and the growth of the diagnostic explosion energy is slower. Our results suggest
 that shock revival and explosion in the 3D simulation may be delayed until sufficiently large plumes form, whereas such plumes form more rapidly in 2D, permitting earlier explosions.

\paragraph{GPU work.}
%
We continued to make substantial progress on offloading the
microphysics in our codes to the GPUs using OpenACC.  Our focus is to
put the nuclear reaction networks onto the GPUs, since they are local,
compute-heavy, standalone physics solvers that take an appreciable
amount of our runtime. Our strategy is to put the entire integration,
the ODE timestepping driver and evaluation of the righthand-side and
Jacobian onto the GPUs.  Previously we demonstrated a speed-up when
using a simple network and a first-order backward-difference
integration scheme.  This past year, we have worked closely with OLCF
staff, including participating in a GPU hackathon, and have our
high-order integrators working on the GPUs, including a production unit test
demonstrating a 2x speedup versus perfect OpenMP (16 threads).  Our collaboration
with OLCF continues, Co-I Jacobs will be traveling to OLCF next week
to work on profiling on the GPUs to understand branching issues and
further the optimization.  In addition, our development of \flash\ for GPU architectures is 
directly supported by a CAAR award at OLCF. This work has already produced a 18x speedup 
on Titan versus the previous unthreaded burning module in \flash\, making large network
runs with the code possible. Importantly, {\it exactly} the same network is used in \chimera\ as well, 
in direct support of our simulation target for CCSNe in this proposal. 

\subsection{Significance of our proposed work}

%% To advance the state of the knowledge of SNe Ia, XRBs, BWPs, and
%% ccSNe, we will carry out the following sets of simulations (all in
%% 3D):
%% \begin{tightitem}
%% \item \castro\ simulations of WD mergers and collisions.
%% \item Full star \maestro\ sub-Ch models with detailed nucleosynthesis
%%   and realistic initial models.
%% \item \maestro\ simulations of convective Urca in WDs
%% \item \flash\ simulations of the explosion of sub-Ch model
%% \item The largest-domain-to-date 3D resolved \maestro\ XRB convection
%%   calculations.
%% \item \castro\ simulations of burning fronts on NSs
%%   as a model for XRB flame propagation
%% \item \castro\ calculations of 
%% \item a large-scale \chimera\ simulation of ccSNe
%% \end{tightitem}

We are the only group in the world modeling the detailed convection
with realistic nuclear physics in XRBs and the sub-Ch SNe Ia.  In all
simulations we will push the size of the nuclear reaction networks to
accurately capture the nucleosynthesis (as discussed later, GPUs will
be used for this task).  

XRBs are important probes of the nuclear equation of state and the
nucleosynthesis that takes place will involve the nuclei that are a
target of the DOE FRIB experiment, the top priority of the Office of
Nuclear Physics.  In addition to modeling the early convective phase,
We will perform the first fully-hydrodynamical calculations of the
spreading of a flame front through a NS atmosphere.  Our simulations
will advance our understanding on the burning dynamics and tell us (1)
whether any burning products can be carried to the photosphere,
altering the interpretation of observations; (2) how the full 3D
treatment of convection modifies the nucleosythesis, allowing us to
provide feedback to the 1D modelers; (3) how to create a sub-grid
model to enable larger scale simulations; and (4) start to learn how
turbulence in the burning alters the spreading of the front across the
NS.  With \maestro\ and \castro, we are in the unique
position to address each of these points.

While several groups are investigating explosions in the sub-Ch model,
we are the only group that is modeling the 3D convective field and
ignition that precedes the explosion.  Much like our previous INCITE
work in carrying \maestro\ convection calculations of the Chandra
model into the explosion phase with \castro, our similar work here for
the sub-Ch model will be unmatched.  We will extend our current suite
of calculations of convection in sub-Ch WDs to use more accurate
reaction networks and realistic initial models.  We will also add
better diagnostics, including using Lagrangian particles for tracing.
Ultimately, we will answer the question of which configurations (WD
mass and He mass) lead to detonations (not just ignition) and
therefore are feasible models for SNe Ia.  The larger reaction network
is is key, as the exact composition of the helium layer at detonation
can have profound effects on the subsequent observations, impacting
the model's viability as a SNe Ia progenitor~\cite{kromer:2010}.  All
simulations will be 3D and model the entire star.

Explosion calculations using \flash\ (and perhaps \castro\ using the
\maestro\ models as starting conditions) will complement these studies
to understand the explosion mechanism itself, informed from the
details of the igniton location and timing we learn from the
convection calculations.
 
Several groups are pursuing WD mergers and collisions, as these seem  \MarginPar{Max--go over this, a few refs if needed}
to be promising candidates for SNe Ia.  The majority of these have
used smoothed particle hydrodynamics (SPH), a gridless alternative to
the methods we use here.  SPH is known to have trouble capturing
instabilities and has low resolution in regions of low
density---precisely the regions where the stars make contact.  Our
grid--based simulations will provide an important counterpart to
existing simulations.  With the power of AMR, we are pushing far
beyond the resolutions of previous grid-based simulations.  Our
\castro\ investigations~\cite{katz:2016}  achieve the highest
resolution every used by grid-based codes.  

In CCSNe, the character of both the Stationary Accretion Shock
Instability (SASI) and neutrino-driven convection in 2D CCSNe
simulations are different than 3D. The nature of the buoyant engine,
including its viability, are unknown for symmetry-free 3D
configurations across the initial mass function. The SASI is confined
to the sloshing mode by axisymmetry and turbulent convection develops
unrealistically large and strong convective rolls, both of which may
work to reinforce the other and result in more stable accretion
streams and a strong buoyant engine.  Some recent simulations using
highly simplified neutrino treatments have suggested that 3D
is the key to more robust explosions, while other similar
simulations have shown the opposite. Our recent 3D simulations
\citep{lentzetal2015} include fully consistent coupling of neutrinos
and the stellar fluid, allowing us to determine how 3D impacts the
nature and strength of the CCSN mechanism. We wish to explore the
lower mass range of the possible set of progenitors for CCSNe in this
proposal. Interestingly, CCSNe progenitors in the mass range below
about 11 solar masses may well rely on significant nuclear burning
during collapse and shock propagation. These conditions are another
excellent candidate for out large-network technology in \chimera.



%-----------------------------------------------------------------------------
\section{RESEARCH OBJECTIVES AND MILESTONES }  

%% Describe the proposed research, including its goals, milestones and
%% the theoretical and computational methods it employs. Goals and
%% milestones should articulate simulation and developmental objectives
%% and be sufficiently detailed to assess the progress of the project for
%% each year of any allocation granted. Milestones should correlate with
%% those in the milestone table. It is especially important that you
%% provide clear connections between the project's overarching
%% milestones, the planned production simulations, and the compute time
%% expected to be required for these simulations (e.g., should correlate
%% with those in the ``Use of Resources Requested'' section below). {\bf
%%   This section is typically about 6 pages.}

\input objectives


%-----------------------------------------------------------------------------
\input readiness

%-----------------------------------------------------------------------------

\bibliographystyle{unsrtnat}
%\begin{multicols}{2}
\bibliography{refs}
%\end{multicols}



\end{document}
