\documentclass[11pt,letterpaper,english]{article}
\usepackage[T1]{fontenc} % Standard package for selecting font encodings
\usepackage{txfonts} % makes spacing between characters space correctly
\usepackage{xcolor} % Driver-independent color extensions for LaTeX and pdfLaTeX.

\usepackage{fancyhdr} % header footer placement

\usepackage[top=1in, bottom=1in, left=1in, right=1in] {geometry} % Margins
\usepackage{graphicx}  % Essential for adding images to you document.

\usepackage{sectsty}
\sectionfont{\normalsize}
\subsectionfont{\normalsize}
\subsubsectionfont{\normalsize \it}


\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}%

\pagestyle{fancy} % allows you to use the header and footer commands


\begin{document}

\setlength{\parindent}{0in} % Amount of indentation at the first line of a paragraph.


\pagestyle{fancy} 
\lhead{Approaching Exascale Models of Astrophysical Explosions} 
\rhead{PI: Zingale} \renewcommand{%
\headrulewidth}{0.0pt}

\begin{center}
{\bf PUBLICATIONS RESULTING FROM INCITE AWARDS} \\
(last three years only)
\end{center}

\begin{itemize}

                                                                               
\item {\em Low Mach Number Modeling of Convection in Helium Shells on
  Sub-Chandrasekhar White Dwarfs II: Bulk Properties of Simple Models,
} A.~M.~Jacobs, M.~Zingale, A.~Nonaka, A.~S.~Almgren, \& J.~B.~Bell
  2016, accepted to ApJ

\item {\em Double White Dwarf Mergers on Adaptive Meshes
  I. Methodology and Code Verification, } M.~P.~Katz, M.~Zingale,
  A.~C.~Calder, F.~D.~Swesty, A.~S.~Almgren, W.~Zhang 2016, ApJ, 819,
  94.

\item {\em Comparisons of Two- and Three-Dimensional Convection in
  Type I X-ray Bursts} M.~Zingale, C.~M.~Malone, A.~Nonaka,
  A.~S.~Almgren, \& J.~B.~Bell 2015, ApJ, 807, 60.

\item {\em Multidimensional Modeling of Type I X-ray
  Bursts. II. Two-Dimensional Convection in a Mixed H/He Accretor, }
  C.~M.~Malone, M.~Zingale, A.~Nonaka, A.~S.~Almgren, \& J.~B.~Bell
  2014, ApJ, 788, 115.

\item {\em Type Ia Supernovae from Merging White
  Dwarfs. II. Post-merger Detonations}, Raskin, C., Kasen, D., Moll,
  R., Schwab, J., \& Woosley, S.~E., 2014, ApJ, 788, 75

\item {\em Type Ia Supernovae from Merging White Dwarfs. I. Prompt Detonations},
  Moll, R., Raskin, C., Kasen, D., \& Woosley, S.~E., 2014, ApJ, 785, 105

\item {\em The Deflagration Stage of Chandrasekhar Mass Models for
  Type Ia Supernovae. I. Early Evolution}, Malone, C. M., Nonaka, A.,
  Woosley, S.~E., Almgren, A.~S., Bell, J.~B., Dong, S., \& Zingale, M.,
  2014, ApJ, 782, 11

\item {\em The Multi-dimensional Character of Core-collapse Supernovae}, Hix, W.R., Lentz, E.J., Bruenn, S.W.,  Mezzacappa, A.,  Messer, O.E.B.,  Endeve, E.,  Blondin, J.M.,  Harris, J.A., Marronetti, P., \&  Yakunin, K.N., 2016, Acta Physica Polonica B, 47, 645.


\item {\em The Development of Explosions in Axisymmetric Ab Initio Core-collapse Super- nova Simulations of 12-25 M$_\odot$   Stars}, Bruenn, Stephen W.,  Lentz, Eric J., Hix, W. Raphael, Mezzacappa, Anthony,  Harris, J. Austin,  Messer, O. E. Bronson,  Endeve, Eirik,  Blondin, John M., Chertkow, Merek Austin, Lingerfelt, Eric J., Marronetti, Pedro,  \&d Yakunin, Konstantin N., 2016, The Astrophysical Journal, 818, 123.


\item {\em Three-Dimensional Core-Collapse Supernova Simulated Using a 15 M$_\odot$   Progenitor}, Lentz, E.J., Bruenn, S.W., Hix, W.R., Mezzacappa, A.,  Messer, O.E.B., Endeve, E., Blondin, J.M., Harris, J.A., Marronetti, P., \& Yakunin, K.N.,  2015, The Astrophysical Journal Letters, 807, L31.


\item {\em Advancing Nucleosynthesis in Self-consistent, Multidimensional Models of Core-Collapse Supernovae}, Harris, J.A., Hix, W.R., Chertkow, M.A., Bruenn, S.W., Lentz, E.J., Messer, O.E.B., Mezzacappa, A.,  Blondin, J.M., Marronetti, P., \& Yakunin, K.N., 2014, In Nuclei in the Cosmos (NIC XIII).


\item {\em Multidimensional simulations of core-collapse supernovae and implications for nucleosynthesis}, Hix, W.R., Harris, J.A., Lentz, E.J., Bruenn, S.W., Chertkow, M.A., Messer, O.E.B., Mezzacappa, A., Endeve, E., Blondin, J.M., Marronetti, P., \& Yakunin, K.N., 2014, In Nuclei in the Cosmos (NIC XIII).


\item {\em Near Real-time Data Analysis of Core-Collapse Supernova Simulations with Bellerophon}, Lingerfelt, E.J., Messer, O.E.B., Desai, S.S.,  Holt, C.A.,  \& Lentz, E.J., 2014, Procedia Computer Science 29, 1504, 2014 International Conference on Computational Science.



\end{itemize}

\end{document}
